Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-13 paper.tex
ADD links

The feasible Q-test, generalized to less restrictive assumptions, is implemented in the R programming language of the \citet{R} following the steps proposed by \citet{campbell2005implementing}\footnote{The source code is available at https://github.com/jpwoeltjen/PersistentRegressors/tree/master/pr.}. Suppose the regressor follows an $AR(p)$ process. Further, the innovations are not necessarily normally distributed but are a martingale difference sequence, i.e., 
\begin{equation}
\mathrm{E}\left[w_{t} |\mathscr{F}_{t-1}\right]=0,
\end{equation}
where $\mathscr{F}_{t}=\left\{w_{s} | s \leq t\right\}$ denotes the filtration generated by $w_{t}=\left(u_{t}, e_{t}\right)^{\prime}$.
Its fourth moments are assumed to be finite and the unconditional variance is fixed, i.e.,
\begin{equation}
\label{eqn:covarst}
\begin{array}{l}{\mathrm{E}\left[w_{t} w_{t}^{\prime}\right]=\Sigma} \\ {\sup _{t} \mathrm{E}\left[u_{t}^{4}\right]<\infty, \sup _{t} \mathrm{E}\left[t_{t}^{4}\right]<\infty, \text { and } \mathrm{E}\left[x_{0}^{2}\right]<\infty.}\end{array}
\end{equation}
The dynamics of $x_{t}$ are written as
\begin{equation}
\label{eqn:22}
x_{t}=\gamma+\rho x_{t-1}+v_{t},
\end{equation}
where $\rho$ is the largest autoregressive root and $b(L) v_{t}=e_{t}$ with $b(L)=\sum_{i=0}^{p-1} b_{i} L^{i}$, $b_{0}=1$, and $b(1) \neq 0$. In this generalized case, the Q-statistic is not asymptotically standard normal distributed under the null. This is corrected by modifying it to
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\sigma_{u e} /\left(\sigma_{e} \omega\right)\left(x_{t}-\rho x_{t-1}\right)\right]+\frac{T}{2} \sigma_{u e} /\left(\sigma_{e} \omega\right)\left(\omega^{2}-\sigma_{v}^{2}\right)}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}},
\end{equation}
where $\omega=\sigma_{e} / b(1)$.

>>>>

The feasible Q-test, generalized to less restrictive assumptions, is implemented in the R programming language of the \citet{R} following the steps proposed by \citet{campbell2005implementing}.\footnote{The source code is available at https://github.com/jpwoeltjen/PersistentRegressors/tree/master/pr.} Suppose the regressor follows an $AR(p)$ process. Further, the innovations are not necessarily normally distributed but are a martingale difference sequence, i.e., 
\begin{equation}
\mathrm{E}\left[w_{t} |\mathscr{F}_{t-1}\right]=0,
\end{equation}
where $\mathscr{F}_{t}=\left\{w_{s} | s \leq t\right\}$ denotes the filtration generated by $w_{t}=\left(u_{t}, e_{t}\right)^{\prime}$.
Its fourth moments are assumed to be finite and the unconditional variance is fixed, i.e.,
\begin{equation}
\label{eqn:covarst}
\begin{array}{l}{\mathrm{E}\left[w_{t} w_{t}^{\prime}\right]=\Sigma} \\ {\sup _{t} \mathrm{E}\left[u_{t}^{4}\right]<\infty, \sup _{t} \mathrm{E}\left[t_{t}^{4}\right]<\infty, \text { and } \mathrm{E}\left[x_{0}^{2}\right]<\infty.}\end{array}
\end{equation}
The dynamics of $x_{t}$ are written as
\begin{equation}
\label{eqn:22}
x_{t}=\gamma+\rho x_{t-1}+v_{t},
\end{equation}
where $\rho$ is the largest autoregressive root and $b(L) v_{t}=e_{t}$ with $b(L)=\sum_{i=0}^{p-1} b_{i} L^{i}$, $b_{0}=1$, and $b(1) \neq 0$. In this generalized case, the Q-statistic is not asymptotically standard normal distributed under the null. This is corrected by modifying it to
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\sigma_{u e} /\left(\sigma_{e} \omega\right)\left(x_{t}-\rho x_{t-1}\right)\right]+\frac{T}{2} \sigma_{u e} /\left(\sigma_{e} \omega\right)\left(\omega^{2}-\sigma_{v}^{2}\right)}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}},
\end{equation}
where $\omega=\sigma_{e} / b(1)$.
